Assessing the Impact of Financial Assistance on Business and Income Outcomes: A Gender-Specific Analysis

### 2024-02-15 paper/paper.qmd
Revise Paper.qmd

---
title: "Assessing the Impact of Financial Assistances on Business and Income Outcomes: A Gender-Specific Analysis"
author: Dingning Li, Yiming Tang, Yingqi Pang 
abstract: "This study replicates and extends the investigation into the differential impacts of financial support on microenterprise performance, considering the gender of entrepreneurs. Analyzing data from 3,294 entrepreneurs, we explored the impact of loans, cash grants, and in-kind grants on business ownership, assets, and profitability, while accounting for personal characteristics. We found that all forms of financial support positively affect microenterprise growth, but in-kind grants are particularly beneficial, especially for female entrepreneurs. This research points to the importance of customizing financial interventions to consider gender, aiming to support economic empowerment and microenterprise resilience.
date: “`r format(Sys.time(), '%d %B %Y')`”
format: pdf
---

@@

# Experiment 
// TODO: Table 1: Baseline Balance of Variables Across Treatment Status

This experiment appears to have been designed to assess the influence of four treatments on a range of business-related outcomes. The process of randomization was employed to ensure that each participant in the experiment had an equal chance being assigned to any treatment groups. This methodological choice that facilitates the balancing of known and unknown mixing variables in these groups. Table 1 provided suggest that this randomization process was successful, as indicated by the balance check labeled “TRUE”. It confirms that the baseline characteristics were evenly distributed among the different treatment groups. This implies that any subsequent differences can be attributed to the effects of the treatments confidently rather than pre-existing differences among participants.

@@

@@

@@

@@

//TODO: Figure 1: Female Monthly Profit vs. Male Monthly Profit

@@

//TODO: Figure 1.2: Female New Asset vs. Male New Asset

@@

@@

//TODO: Table 4.1: Impacts of Financial Supports on Income Outcomes Among Female Participants

//TODO: Table 4.2: Impacts of Financial Supports on Income Outcomes Among Male Participants

>>>>

---
title: "Assessing the Impact of Financial Assistance on Business and Income Outcomes: A Gender-Specific Analysis"
author: "Dingning Li, Yiming Tang, Yingqi Pang"
abstract: "This study replicates and extends previous research on the differential impacts of financial support on microenterprise performance, with a focus on the entrepreneurs' gender. By analyzing data from 3,294 entrepreneurs, we explored the effects of loans, cash grants, and in-kind grants on business ownership, assets, and profitability, while taking personal characteristics into account. Our findings suggest that all forms of financial assistance positively influence microenterprise growth, with in-kind grants being particularly advantageous, especially for female entrepreneurs. This research underscores the importance of tailoring financial interventions to consider gender differences, aiming to promote economic empowerment and enhance microenterprise resilience."
date: "`r format(Sys.time(), '%d %B %Y')`"
format: pdf
---

@@

# Experiment 
// TODO: Table 1: Baseline Balance of Variables Across Treatment Status
This experiment appears to have been designed to assess the influence of four treatments on a range of business-related outcomes. The process of randomization was employed to ensure that each participant in the experiment had an equal chance being assigned to any treatment groups. This methodological choice that facilitates the balancing of known and unknown mixing variables in these groups. Table 1 provided suggest that this randomization process was successful, as indicated by the balance check labeled “TRUE”. It confirms that the baseline characteristics were evenly distributed among the different treatment groups. This implies that any subsequent differences can be attributed to the effects of the treatments confidently rather than pre-existing differences among participants.

::: {.figure}
![Baseline Balance](../outputs/tables/baseline_balance.png){width=99%}
:::

@@

::: {.figure}
![Business Outcome](../outputs/tables/business_outcome.png){width=99%}
:::

@@

::: {.figure}
![](../outputs/tables/business_outcome_female.png){width=99%}
:::

@@

::: {.figure}
![](../outputs/tables/business_outcome_male.png){width=99%}
:::

@@

@@

::: {.figure}
![Female Monthly Profit](../outputs/figures/femaleFemale - Monthly Profit.jpg){width=49%}
![Male Monthly Profit](../outputs/figures/maleMale - Monthly Profit.jpg){width=49%}
:::

@@

::: {.figure}
![Female Monthly Profit](../outputs/figures/femaleFemale - New Asset.jpg){width=49%}
![Male Monthly Profit](../outputs/figures/maleMale - New Asset.jpg){width=49%}
:::

@@

//TODO: Table 4.1: Impacts of Financial Supports on Income Outcomes Among Female Participants
```{=latex}
\input{../outputs/tables/income_outcome_female.tex}
```

//TODO: Table 4.2: Impacts of Financial Supports on Income Outcomes Among Male Participants
```{=latex}
\input{../outputs/tables/income_outcome_male.tex}
```
